---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

[TEXT IN SQUARE BRACKETS IS HERE FOR GUIDANCE. PLEASE DELETE TEXT IN SQUARE BRACKETS BEFORE KNITTING THE FINAL REPORT]

# Report Details

[PILOT/COPILOT ENTER RELEVANT REPORT DETAILS HERE]

```{r}
articleID <- "2-10-2014" # insert the article ID code here e.g., "10-3-2015"
reportType <- "pilot" # specify whether this is the 'pilot' report or 'copilot' report
pilotNames <- "Ethan Roy" # insert the pilot's name here e.g., "Tom Hardwicke".
copilotNames <- "Justin Yuan" # # insert the co-pilot's name here e.g., "Michael Frank".
pilotTTC <- NA # insert the pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
copilotTTC <- NA # insert the co-pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
pilotStartDate <- as.Date("10/30/18", format="%m/%d/%y") # insert the piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- as.Date("11/9/19", format = "%m/%d/%y")# insert the co-piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- NA # insert the date of final report completion in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

------

#### Methods summary: 

[PILOT/COPILOT write a brief summary of the methods underlying the target outcomes written in your own words]

This study recruited 135 undergraduate students to participate in a two part survey. At Time 1 (the beginning of the summer), the participants created "time capsules", which encompassed a range of current or recent experiences. These experiences included, but was not limited to, things like the last social event they attended, the last three songs they listened to, an inside joke, and a question from a recent final exam. After curating their time capsules, the participants were asked to predict how curious they would be to see what they included, how surprised they would be by each element, and how meaningful and interesting they would find each element in the future. All predictions were made on a scale of 1 (not at all) to 7 (extremely).

Three months later (Time 2), the participants recieved a follow-up survey that listed the prompts they saw at Time 1. Before seeing their original submissions to the "time capsule", participants were asked to indicate how curious they were to see their response to each prompt. After viewing their submissions from Time 1, partipants rated how surprised they were and how meaningful and interseting they found each item in their "time capsule". 

------

#### Target outcomes: 

For this article you should focus on the findings reported in the results section for Study 1 (and Table 1).

Specifically, you should attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Table 1 provides descriptive statistics for each measure
for Study 1.

> Participants’ Time 1 predictions of their curiosity (M = 3.99, SD = 1.32) were lower than their actual curiosity ratings at Time 2, immediately before reading their responses (M = 4.34, SD = 1.25), t(105) = 2.88, p = .005, d = 0.27. Participants also underestimated how interesting they would find their responses. Predictions of interest at Time 1 (M = 3.54, SD = 1.01) were lower than ratings of actual interest experienced at Time 2 (M = 3.82, SD = 0.89), t(105) = 3.10, p = .003, d = 0.29.

------

[PILOT/COPILOT DO NOT CHANGE THE CODE IN THE CHUNK BELOW]  

```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages and prepare report object

[PILOT/COPILOT Some useful packages are being loaded below. You can add any additional ones you might need too.]

```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
library(effsize) # to calculate effect size
```

[PILOT/COPILOT DO NOT MAKE CHANGES TO THE CODE CHUNK BELOW]

```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r}

data = read_sav("/Users/Ethan/Documents/Stanford/Fall 2019/PSYCH 251/reproducibility_assignment/GroupC_2-10-2014/data/Study1_Data.sav")

data

```

# Step 3: Tidy data

**Using included means**
```{r}

#used means found in data file (gets numbers that match original paper)

#rename Interest Composite column to avoid issues while splitting column later
colnames(data)[colnames(data)=="T1_Interest_Composite"]<-"T1_InterestComposite"
colnames(data)[colnames(data)=="T2_Interest_Composite"]<-"T2_InterestComposite"

tidyMeanData<-data %>%
  filter(T2_Finished==1) %>%  #exclude participants who didn't finish T2
  gather(Measure, Rating,T1_Curious,T1_Interesting,T1_Meaningful,T1_Surprised,T2_Curious,T2_Interesting,T2_Meaningful,T2_Surprised,T1_InterestComposite,T2_InterestComposite) %>% #gather on the means for each measure
  select(-matches("diff|Song|Roommate|Social|Finals|Essay|Joke|FB|Convo|Photo"),-Gender,-Year_born,-Age) %>% #remove unnecessary columns
  separate(Measure, c("Time", "Measure"),sep="_") #split the Measure column so T1 and T2 are captured in their own column

#since t1 and t2 measures have different capitalization schemes, make them all lowercase
tidyMeanData$Measure <- tolower(tidyMeanData$Measure) 

tidyMeanData
```

**Using raw scores provided:**
```{r}
##Use raw survey data (gets some numbers that are off by .01 of original paper)

tidyRawData<-data %>%
  filter(T2_Finished==1) %>% #exclude participants who didn't finish T2
  select(-matches("Curious_diff|Age|Gender|Year_born|T1_Meaningful|T2_Meaningful|T1_Curious|T2_Curious|T1_Surprised|T2_Surprised|T1_Interesting|T2_interesting|T1_InterestComposite|T2_InterestComposite")) %>% #drop all columns except raw data
  select(-contains("diff")) %>%  #remove the diff columns
  gather(Measure,Rating,contains("Suprised"),contains("surprised"),contains("Curious"),contains("curious"),contains("Interesting"),contains("interesting"),contains("Meaningful"),contains("meaningful"),contains("_composite")) %>%
   separate(Measure,c("Time","Item","Measure")) #split the Measures column into three: a time column, an capsule item column, and a measure column

   tidyRawData$Measure<-tolower(tidyRawData$Measure) #standardize case in Measure column
   tidyRawData$Measure[tidyRawData$Measure=="interest"]<-"interestcomposite" #give the composite interest score a more distinct name
  
 tidyRawData

```

# Step 4: Run analysis

## Pre-processing

**Using included means**
```{r}

#summaries using included means
includedMeans <- tidyMeanData %>%
  group_by(Measure,Time) %>%
  summarise(mean=mean(Rating,na.rm = T),
            sd=sd(Rating,na.rm=T),
            lower=mean(Rating) - (qnorm(0.975)*sd(Rating))/sqrt(n()),
            upper=mean(Rating) + (qnorm(0.975)*sd(Rating))/sqrt(n()))

#make data wide to best match original table
wideIncludedData<- includedMeans %>%
  pivot_wider(names_from=Time,
              values_from=c(mean,sd,lower,upper))

wideIncludedData
```

**Using raw scores provided:**
```{r}
#summaries for raw data
rawMeans<-tidyRawData %>%
  group_by(Measure,Time) %>%
  summarise(mean=mean(Rating,na.rm = T),
            sd=sd(Rating,na.rm=T),
            lower=mean(Rating,na.rm=T) - (qnorm(0.975)*sd(Rating,na.rm=T))/sqrt(n()),
            upper=mean(Rating,na.rm=T) + (qnorm(0.975)*sd(Rating,na.rm=T))/sqrt(n()))

#make data wide to best match original table
wideRawData<- rawMeans %>%
  pivot_wider(names_from=Time,
              values_from=c(mean,sd,lower,upper))

wideRawData


```

## Descriptive statistics

### Recreation of Table 1 from original paper:

**Using included means**

```{r}

#reformat included data table
wideIncludedData<-wideIncludedData[c("Measure","mean_T1","lower_T1","upper_T1","sd_T1","mean_T2","lower_T2","upper_T2","sd_T2")] %>% 
  mutate(Underestimate=mean_T2-mean_T1) #add underestimate column

wideIncludedData
```

**Using raw scores provided:**
```{r}
#reformat raw data table
wideRawData<-wideRawData[c("Measure","mean_T1","lower_T1","upper_T1","sd_T1","mean_T2","lower_T2","upper_T2","sd_T2")] %>% 
  mutate(Underestimate=mean_T2-mean_T1) #add underestimate column

wideRawData
```

## Inferential statistics

### Using the means included in the original dataset
**Curiousity Measure:**

```{r}


#Run t-tests with means inlcuded in original data set

filteredData=data %>%
    filter(T2_Finished==1)

#create array with p-values for various measures
pvals=c(t.test(filteredData$T2_Curious,filteredData$T1_Curious,paired=T)$p.value,
t.test(filteredData$T2_InterestComposite,filteredData$T1_InterestComposite,paired=T)$p.value,
t.test(filteredData$T2_Interesting,filteredData$T1_Interesting,paired=T)$p.value,
t.test(filteredData$T2_Meaningful,filteredData$T1_Meaningful,paired=T)$p.value,
t.test(filteredData$T2_Surprised,filteredData$T1_Surprised,paired=T)$p.value)

#add pval column to table
wideIncludedData$pVals=pvals


##Included Data ReproChecks
curiousityincludedMeanCheck1<- reproCheck(reportedValue = '3.99', obtainedValue = wideIncludedData$mean_T1[1], valueType = 'mean')

curiousityIncludedSDCheck1<-reproCheck(reportedValue = '1.32', obtainedValue = wideIncludedData$sd_T1[1], valueType = 'sd')

curiousityIncludedMeanCheck2<- reproCheck(reportedValue = '4.34', obtainedValue = wideIncludedData$mean_T2[1], valueType = 'mean')

curiousityIncludedSDCheck2<-reproCheck(reportedValue = '1.25', obtainedValue = wideIncludedData$sd_T2[1], valueType = 'sd')

curiousityIncludedTCheck<- reproCheck(reportedValue = '2.88', obtainedValue = t.test(filteredData$T2_Curious,filteredData$T1_Curious,paired=T)$statistic, valueType = 't')

curiousityIncludedPCheck <- reproCheck(reportedValue = '.005', obtainedValue = wideIncludedData$pVals[1], valueType = 'p')

curiousityIncludedDCheck <- reproCheck(reportedValue = '0.27', obtainedValue=cohen.d(filteredData$T2_Curious,filteredData$T1_Curious,paired=T)$estimate,valueType = 'd')
```

**Composite Interest Measure:**
```{r}
interestIncludedMeanCheck1<- reproCheck(reportedValue = '3.54', obtainedValue = wideIncludedData$mean_T1[2], valueType = 'mean')

interestIncludedSDCheck1<-reproCheck(reportedValue = '1.01', obtainedValue = wideIncludedData$sd_T1[2], valueType = 'sd')

interestIncludedMeanCheck2<- reproCheck(reportedValue = '3.82', obtainedValue = wideIncludedData$mean_T2[2], valueType = 'mean')

interestIncludedSDCheck2<-reproCheck(reportedValue = '0.89', obtainedValue = wideIncludedData$sd_T2[2], valueType = 'sd')

interestIncludedTCheck<- reproCheck(reportedValue = '3.10', obtainedValue = t.test(filteredData$T2_InterestComposite,filteredData$T1_InterestComposite,paired=T)$statistic, valueType = 't')

interestIncludedPCheck <- reproCheck(reportedValue = '.003', obtainedValue = wideIncludedData$pVals[2], valueType = 'p')

interestIncludedDCheck <- reproCheck(reportedValue = '0.29', obtainedValue=cohen.d(filteredData$T2_InterestComposite,filteredData$T1_InterestComposite,paired=T)$estimate,valueType = 'd')
                                    
```

### Using the raw scores from in the original dataset:
**Curiousity Measure:**
```{r}
#run t-tests with means caclulated using raw data

#calculate means for each measure at T1 and T2
statsData<-tidyRawData %>% 
  group_by(Order,Measure,Time) %>% 
  summarise(mean=mean(Rating,na.rm=T)) %>% 
  unite("Measure",Time:Measure, remove=T) %>%   
  pivot_wider(names_from = Measure, values_from = mean)

#create array with p-values for various measures
pvals=c(t.test(statsData$T2_curious,statsData$T1_curious,paired=T)$p.value,
t.test(statsData$T2_interestcomposite,statsData$T1_interestcomposite,paired=T)$p.value,
t.test(statsData$T2_interesting,statsData$T1_interesting,paired=T)$p.value,
t.test(statsData$T2_meaningful,statsData$T1_meaningful,paired=T)$p.value,
t.test(statsData$T2_surprised,statsData$T1_surprised,paired=T)$p.value)

#add pval column to table
wideRawData$pVals=pvals

##Raw Data ReproChecks
curiousityrawMeanCheck1<- reproCheck(reportedValue = '3.99', obtainedValue = wideRawData$mean_T1[1], valueType = 'mean')

curiousityrawSDCheck1<-reproCheck(reportedValue = '1.32', obtainedValue = wideRawData$sd_T1[1], valueType = 'sd')

curiousityrawMeanCheck2<- reproCheck(reportedValue = '4.34', obtainedValue = wideRawData$mean_T2[1], valueType = 'mean')

curiousityrawSDCheck2<-reproCheck(reportedValue = '1.25', obtainedValue = wideRawData$sd_T2[1], valueType = 'sd')

curiousityrawTCheck<- reproCheck(reportedValue = '2.88', obtainedValue = t.test(statsData$T2_curious,statsData$T1_curious,paired=T)$statistic, valueType = 't')

curiousityrawPCheck <- reproCheck(reportedValue = '.005', obtainedValue = wideRawData$pVals[1], valueType = 'p')

# stuff=c(mean_T2[1],mean_T1[2])

curiousityRawdDCheck <- reproCheck(reportedValue = '0.27', obtainedValue=cohen.d(statsData$T2_curious,statsData$T1_curious,paired=T,na.rm=T)$estimate,valueType = 'd')
```

**Composite Interest Measure:**
```{r}
interestrawMeanCheck1<- reproCheck(reportedValue = '3.54', obtainedValue = wideRawData$mean_T1[2], valueType = 'mean')

interestrawSDCheck1<-reproCheck(reportedValue = '1.01', obtainedValue = wideRawData$sd_T1[2], valueType = 'sd')

interestrawMeanCheck2<- reproCheck(reportedValue = '3.82', obtainedValue = wideRawData$mean_T2[2], valueType = 'mean')

interestrawSDCheck2<-reproCheck(reportedValue = '0.89', obtainedValue = wideRawData$sd_T2[2], valueType = 'sd')

interestrawTCheck<- reproCheck(reportedValue = '3.10', obtainedValue = t.test(statsData$T2_interestcomposite,statsData$T1_interestcomposite,paired=T)$statistic, valueType = 't')

interestRawPCheck <- reproCheck(reportedValue = '.003', obtainedValue = wideRawData$pVals[2], valueType = 'p')

interestRawdDCheck <- reproCheck(reportedValue = '0.29', obtainedValue=cohen.d(statsData$T2_interestcomposite,statsData$T1_interestcomposite,paired=T,na.rm=T)$estimate,valueType = 'd')


```

# Step 5: Conclusion

When I used the mean data that was included with the original data set, I was able to reproduce all of the statistics reported in the original study. However, when I used the raw scores from the data set, some of the statistics differed from the orginal study. Though I was able to match the t-score and p-value using the raw scores, the means and standard deviations differed slightly from the values reported by the original authors. Based on the format of the provided dataset, it seems that the original analysis was conducted using SPSS and there may have been some differences in rounding between R and SPSS which led to these observed diferences.

[PILOT/COPILOT DOD NOT EDIT THE CODE CHUNK BELOW]

```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
